Evolution of solar wind discontinuities in the inner heliosphere

### 2025-01-24 index.qmd
chore: cleanup

### High-speed solar wind radial evolution

:::: {.columns}
::: {.column}
![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR.svg)

![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-next.svg)

![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-previous.svg)
:::

::: {.column}

![](images/sty3348fig5.jpeg)

@perroneRadialEvolutionSolar2019
:::
::::

::: {.notes}
The radial dependence of the proton number density, $n_p$ and magnetic ﬁeld magnitude, $B$, is given by

$$
n_p = (2.4 ± 0.1)(R/R_0)^{−(1.96±0.07)} cm^{−3}
\\
B = (5.7 ± 0.2)(R/R_0)^{−(1.59±0.06)} nT
$$

The faster decrease of the magnetic than kinetic pressure is reﬂected in the radial proton plasma beta variation

$$
β_p = P_k/P_B = (0.55 ± 0.04)(R/R_0)^{(0.4±0.1)}
$$ 
:::

@@

## Comparison between Alfven speed and plasma speed change

@@

## Estimated Anisotropy

@@

>>>>

@@

## Alfvénicity

Comparison between Alfven speed and plasma speed change

@@

### Estimated Anisotropy

@@

# Appendix

### 2025-01-24 notes.qmd
chore: cleanup

- [x] Why ARTEMIS electron data and Wind ion data?
- [ ] Disagreement between anisotropy observed and predicted by the theory
  - maybe just too localized anisotropy that is not well measured with available time resolution... 
  - or maybe more complex ion distribution, where nongyrotropy is more important than anisotropy
# TODO

@@

>>>>

- [x] Why ARTEMIS electron data and Wind ion data?
- [ ] Disagreement between anisotropy observed and predicted by the theory
  - maybe just too localized anisotropy that is not well measured with available time resolution... 
  - or maybe more complex ion distribution, where nongyrotropy is more important than anisotropy

# TODO

@@

## High-speed solar wind radial evolution

:::: {.columns}
::: {.column}
![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR.svg)

![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-next.svg)

![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-previous.svg)
:::

::: {.column}

![](images/sty3348fig5.jpeg)

@perroneRadialEvolutionSolar2019
:::
::::

::: {.notes}
The radial dependence of the proton number density, $n_p$ and magnetic ﬁeld magnitude, $B$, is given by

$$
n_p = (2.4 ± 0.1)(R/R_0)^{−(1.96±0.07)} cm^{−3}
\\
B = (5.7 ± 0.2)(R/R_0)^{−(1.59±0.06)} nT
$$

The faster decrease of the magnetic than kinetic pressure is reflected in the radial proton plasma beta variation

$$
β_p = P_k/P_B = (0.55 ± 0.04)(R/R_0)^{(0.4±0.1)}
$$ 
:::
